---
title: "WUP_04"
author: "Quintin Burnett"
date: "fall 2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
GSScsv <- read_csv("GSScsv.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Mention that you intend to use chatGPT to the greatest extent possible. Give credit to chatGPT when you use it to create code in your report. Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
basicCN <- ggplot(GSScsv,aes(x=DEGREE,y=WORDSUM))
```

```{r}
basicCN + geom_boxplot()
```
There seems to be a noticeable difference in scores on the DEGREE category. The first quartile of the GRADUATE category is much higher than the third quartile of the HIGH SCHOOL category. JUNIOR COLLAGE category's first quartile is also higher than LT HIGH SCHOOL category.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(WORDSUM~DEGREE,data=GSScsv)
```
GRADUATE has the highest average in the dataset. GRADUATE 1st quartile is 10 while LT HIGH SCHOOL 3rd quartile is 8.25 and HIGH SCHOOL 9. HIGH SCHOOL	category has about the same amount of people as all the other numbers combined. The difference is significant when looking at the number of people.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfies the assumptions and is appropriate to answer the research question! Write at the 98th percentile confidence level not the 95th!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
